Reproducibility of published meta-analyses on clinical psychological interventions

### 2023-04-21 response_letter.Rmd

# Reviewer \#3

\RC{- I think the reporting of results in the abstract could be imrpoved. Currently it states that 52 reanlysis results showed a discrepancy larger than 5\% from the original results - I think that sounds far more concerning that it actually is given that there were very few 'decision errors' and the authors believe that the reproducibiltiy issues had "little or no effect" on the original conclusions. So I think its worth stating that in the abstract to avoid any miscommunications. The point at which the authors 'qualitative assessment' and the input from the original authors is also not clear in the abstract.}

We agree that this is something that deserves to be mentioned in the abstract. We have added two sentences to the abstract:

>Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data. The original data were retrieved for 146 \textcolor{blue}{(67\%, 146/217)} meta-analyses. Of these, 52 showed a discrepancy larger than 5% in the main results in the first stage. \textcolor{blue}{For 10 meta-analyses this discrepancy was solved after fixing a coding error and for 15 of them it was considered approximately reproduced in a qualitative assessment.} In the remaining 27 meta-analyses \textcolor{blue}{(18\%, 27/146)}, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of data, or transcription errors. \textcolor{blue}{Nevertheless, the numerical discrepancies were mostly minor, with little or no impact on the conclusions.} Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data. The implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.

### 2023-04-21 submission.Rmd
Revised version

abstract: |
  Meta-analysis is one of the most useful and powerful research approaches, the relevance of which relies on its credibility. However, in recent years different concerns about the credibility of psychological research have emerged. Reproducibility of scientific results could be considered as the minimal threshold of it.  In this study, our purpose was to assess the  reproducibility of a sample of published meta-analyses. From a random sample of 100 papers containing at least one meta-analysis on the effectiveness of interventions in clinical psychology, 217 meta-analyses were selected. We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc), or requesting it from original authors. Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data. The original data were retrieved for 146 \textcolor{blue}{(67\%, 146/217)} meta-analyses. Of these, 52 showed a discrepancy larger than 5% in the main results in the first stage. \textcolor{blue}{For 10 meta-analyses this discrepancy was solved after fixing a coding error and for 15 of them it was solved with minor adjustment or considered approximately reproduced in a qualitative assessment.} In the remaining 27 meta-analyses\textcolor{blue}{(18\%, 27/146)}, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of data, or transcription errors. \textcolor{blue}{Nevertheless, the numerical discrepancies produced by these issues were mostly minor, with little or no impact on the conclusions.} Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data. The implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.

>>>>

abstract: |
  Meta-analysis is one of the most useful research approaches, the relevance of which relies on its credibility. However, in recent years different concerns about the credibility of psychological research have emerged. Reproducibility of scientific results could be considered as the minimal threshold of it. Our purpose was to assess the reproducibility of a sample of published meta-analyses. From a random sample of 100 papers containing at least one meta-analysis on the effectiveness of interventions in clinical psychology, 217 meta-analyses were selected. We first tried to retrieve the original data by recovering a data file, recoding the data from document files, or requesting it from original authors. Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data. The original data were retrieved for 146 \textcolor{blue}{(67\%, 146/217)} meta-analyses. Of these, 52 showed a discrepancy larger than 5% in the main results in the first stage. \textcolor{blue}{For 10 meta-analyses this discrepancy was solved after fixing a coding error and for 15 of them it was considered approximately reproduced in a qualitative assessment.} In the remaining 27 meta-analyses \textcolor{blue}{(18\%, 27/146)}, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of data, or transcription errors. \textcolor{blue}{Nevertheless, the numerical discrepancies were mostly minor, with little or no impact on the conclusions.} Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data. The implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.

### 2023-04-21 submission.tex
Revised version

\abstract{%
Meta-analysis is one of the most useful and powerful research approaches, the relevance of which relies on its credibility. However, in recent years different concerns about the credibility of psychological research have emerged. Reproducibility of scientific results could be considered as the minimal threshold of it. In this study, our purpose was to assess the reproducibility of a sample of published meta-analyses. From a random sample of 100 papers containing at least one meta-analysis on the effectiveness of interventions in clinical psychology, 217 meta-analyses were selected. We first tried to retrieve the original data by recovering a data file, recoding the data from document files (pdf, doc), or requesting it from original authors. Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data. The original data were retrieved for 146 \textcolor{blue}{(67\%, 146/217)} meta-analyses. Of these, 52 showed a discrepancy larger than 5\% in the main results in the first stage. \textcolor{blue}{For 10 meta-analyses this discrepancy was solved after fixing a coding error and for 15 of them it was solved with minor adjustment or considered approximately reproduced in a qualitative assessment.} In the remaining 27 meta-analyses\textcolor{blue}{(18\%, 27/146)}, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of data, or transcription errors. \textcolor{blue}{Nevertheless, the numerical discrepancies produced by these issues were mostly minor, with little or no impact on the conclusions.} Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data. The implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.
}

>>>>

\abstract{%
Meta-analysis is one of the most useful research approaches, the relevance of which relies on its credibility. However, in recent years different concerns about the credibility of psychological research have emerged. Reproducibility of scientific results could be considered as the minimal threshold of it. Our purpose was to assess the reproducibility of a sample of published meta-analyses. From a random sample of 100 papers containing at least one meta-analysis on the effectiveness of interventions in clinical psychology, 217 meta-analyses were selected. We first tried to retrieve the original data by recovering a data file, recoding the data from document files, or requesting it from original authors. Second, through a multi-stage workflow, we tried to reproduce the main results of each meta-analysis using these data. The original data were retrieved for 146 \textcolor{blue}{(67\%, 146/217)} meta-analyses. Of these, 52 showed a discrepancy larger than 5\% in the main results in the first stage. \textcolor{blue}{For 10 meta-analyses this discrepancy was solved after fixing a coding error and for 15 of them it was considered approximately reproduced in a qualitative assessment.} In the remaining 27 meta-analyses \textcolor{blue}{(18\%, 27/146)}, different issues were identified in an in-depth review of the papers, such as reporting inconsistencies, lack of data, or transcription errors. \textcolor{blue}{Nevertheless, the numerical discrepancies were mostly minor, with little or no impact on the conclusions.} Current practices of data sharing in meta-analyses hamper the reusability of meta-analytic data. The implementation of new tools would help to avoid certain errors in the meta-analysis reporting process.
}
